---
title: "Scraping Native-Land.CA for carceral locations"
output: html_notebook
---
Here's an overview on the httr function. 
https://cran.r-project.org/web/packages/httr/vignettes/quickstart.html

First load the CSV. Include headers. 

```{r}
library(httr)

prison_boundaries_centroids...prison_boundaries_centroids <- read.csv("~/Downloads/prison_boundaries_centroids - prison_boundaries_centroids.csv", stringsAsFactors=FALSE) 
```

Check out the structure

```{r}
str(prison_boundaries_centroids...prison_boundaries_centroids)

```

Make the name more manageable

```{r}
dfLand <- prison_boundaries_centroids...prison_boundaries_centroids
```

Make the column into an object

```{r}
 URL <- dfLand$API..click.these..[1]
```


Check that you are going to get some JSON

```{r}
GET(URL)
```

Looks like its working now lets make those responses into an object

```{r}
response <- GET(URL)
```

We can View(response) if you want. But lets move on to seeing the content. 

```{r}
content(response)
```

From this we can see that we want
[[1]]$properties$Name

But let's check

```{r}
content(response) [[1]]$properties$Name
```



```{r}
dfLand$API_Name <- NA

for( i in nrow(dfLand)) {
    message(i)
URL <- dfLand$API..click.these..[i]
response <- GET(URL)
dfLand$API_Name [i] <- content(response)[[1]]$properties$Name  

Sys.sleep(1)

}
```
Its also nice identify yourself:

```{r}
GET("http://httpbin.org/user-agent", user_agent("httr"))
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

